On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-08-24 docs/mvfits_paper/mvf.tex
misc updates

Perhaps most intriguingly, the formal series expansions of smooth functions support linear and rational models (e.g. Pad\'e approximants) having application to many datasets.

@@

Here we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex valued) of many variables.

>>>>

Perhaps most intriguingly, the formal series expansions of smooth functions support linear and rational models (e.g. Pad\'e approximants) that have application to many datasets.

@@

With this in mind, here, we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex valued) of many variables.
